Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-11-16 beamer/envolve.tex
add reinforcement learning
commit after come back

% !TEX root = ../beamer.tex
\section{Manufacturing Ecosystem Envolving}
\subsection{Envolving Aim \& Main Factors}
\begin{frame}{Envolving Aim \& Main Factors}{Manufacturing Ecosystem Envolving}
\onslide<+->{The aim of envolving in the Ecosystem is to: \begin{itemize}
\item optimize the utilize of manufacturing resources
\item find the adaptive operating model for enterprises
\item filter out the underisable enterprises.
\end{itemize}}
\onslide<+->{
\begin{block}{Main Factors for Envolving}
\begin{itemize}
\item Rating Schema;
\item Recommand System and
\item Criterion of User Introduction and Elimination
\end{itemize}
\end{block}}
\end{frame}

\subsection{Rating Schema}
\begin{frame}{Rating Schema}{Manufacturing Ecosystem Envolving}
\onslide<+->{Rating user's rank is the base of Recommand System, so the rating schema should be designed. Most modern rating systems are derived from Elo's model:}
\onslide<+->{\begin{numcases}{}
E_A = \frac{1}{1+10^{\frac{R_B-R_A}{400}}} \\
R_A := R_A + K(S_A - E_A) \\
E_B = \frac{1}{1+10^{\frac{R_A-R_B}{400}}} \\
R_B := R_B + K(S_B - E_B)
\end{numcases}}
\end{frame}

\subsection{Recommand System}
\begin{frame}{Recommand System}{Manufacturing Ecosystem Envolving}
\onslide<+->{There are two scenarios in recommendation:
\begin{itemize}
\item Service Searching
\item Platform priority setting
\end{itemize}
}
\onslide<+->{
	Collaboration Filtering is popular method used in recommand system:
	\begin{equation}
	\begin{split}
	\min_{p_*,q_*,b_*} & \sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 \\
		& + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
	\end{split}
	\end{equation}
	\begin{numcases}{}
	\hat{r}_{ui} = b_{ui} + p^T_uq_i \\
	b_{ui} = \mu + b_u + b_i  \\
	\kappa =\{(u,i)|r_{ui} \text{is known}\} 
	\end{numcases}
}
\end{frame}

\subsection{User Introduction \& Elimination}
\begin{frame}{User Introduction \& Elimination}{Manufacturing Ecosystem Envolving}
\onslide<+->{
	Ecosystem envolving need a good user introduction and elimination method with:
}
\onslide<+->{
	\begin{block}{Envolving}
	\begin{itemize}
	\item Reinforcement Learning
	\item Control
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Envision of the Ecosystem}
\begin{frame}{Envision}{After a long running time and the system seems stable}
\onslide<+->{
	With poper scheduling and envolving, Cloud Manufacturing Ecosystem running with a stable mode:
	\begin{block}{Stable System Envision}
	\begin{itemize}
		\item Less-Popular manufacturing services are utilized instead of idleness with Coupon
		\item Products are manufactured with appropriate resource
		\item High rank users in different type of manufacturing resource lead the industrial chain
		\item Good operating models appear and being refined with time goes by
	\end{itemize}
	\end{block}
}
\end{frame}

>>>>

% !TEX root = ../beamer.tex
\section{Manufacturing Ecosystem Evolution}
\subsection{Evolution Aim \& Main Factors}
\begin{frame}{Envolving Aim \& Main Factors}{Manufacturing Ecosystem Envolving}
\only<1-2>{The evolution  aim in the Ecosystem is to: \begin{itemize}
\item optimize the utilize of manufacturing resources
\item find the adaptive operating model for enterprises
\item filter out the undesirable enterprises.
\end{itemize}}
\only<2>{
\begin{block}{Main Factors for Evolution}
\begin{itemize}
\item Rating Schema;
\item Recommand System;
\item Criterion of User Introduction and Elimination
\end{itemize}
\end{block}}
\only<3>{
	\begin{figure}\centering
		\includegraphics[width =\textwidth]{figures/wanting.png}
		\caption{The Ideal Model of the System}
	\end{figure}
}
\end{frame}

\subsection{Rating Schema}
\begin{frame}{Rating Schema}{Manufacturing Ecosystem Envolving}
\onslide<+->{Rating user's rank is the base of Recommand System, so the rating schema should be designed. Most modern rating systems are derived from Elo's model}
\onslide<+->{\begin{numcases}{}
E_A = \frac{1}{1+10^{\frac{R_B-R_A}{400}}} \\
R_A := R_A + K(S_A - E_A) \\
E_B = \frac{1}{1+10^{\frac{R_A-R_B}{400}}} \\
R_B := R_B + K(S_B - E_B)
\end{numcases}}
\end{frame}

\subsection{Recommand System}
\begin{frame}{Recommandation System}{Manufacturing Ecosystem Evolution}
\onslide<+->{There are two scenarios in recommendation:
\begin{itemize}
\item Service Searching
\item Platform priority setting
\end{itemize}
}
\onslide<+->{
	Collaboration Filtering is a popular method used in recommand system:
	\begin{equation}
	\begin{split}
	\min_{p_*,q_*,b_*} & \sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 \\
		& + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
	\end{split}
	\end{equation}
	\begin{numcases}{}
	\hat{r}_{ui} = b_{ui} + p^T_uq_i \\
	b_{ui} = \mu + b_u + b_i  \\
	\kappa =\{(u,i)|r_{ui} \text{is known}\}
	\end{numcases}
}
\end{frame}

\subsection{User Introduction \& Elimination}
\begin{frame}{User Introduction \& Elimination}{Manufacturing Ecosystem Envolving}
\onslide<+->{
	Ecosystem envolving need a good user introduction and elimination method with:
}
\onslide<+->{
	\begin{block}{Evolution}
	\begin{itemize}
	\item Reinforcement Learning
	\item Control
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Envision of the Ecosystem}
\begin{frame}{Envision}{After a long running time and the system seems stable}
\onslide<+->{
	With poper scheduling and evolution, Cloud Manufacturing Ecosystem running with a stable mode:
	\begin{block}{Stable System Envision}
	\begin{itemize}
		\item Less-Popular manufacturing services are utilization instead of idleness with Coupon
		\item Products are manufactured with appropriate resources
		\item High rank users in different types of manufacturing resource lead the industrial chain
		\item Good operating models improved with time goes by
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Simple Demo} % (fold)
\label{sub:simple_demo}
\begin{frame}{Simple Demo}
\only<1>{
Based on Elo model, we focus on the how sellers' ranks will
change with different specifications.

If we set $Q_A=10^{\frac{R_A}{400}}$ and $Q_B=10^{\frac{R_B}{400}}$, we have:
$$
\begin{cases}
E_A = \frac{Q_A}{Q_A + Q_B}\\
E_B = \frac{Q_B}{Q_B + Q_A}
\end{cases}
$$}
\only<2>{
For entity in the ecosystem(seller) $i,k$ ($i,k=1,2,\dots,n$), we assume that:
$$
\begin{cases}
Q_A = Q_i\\
Q_B = \frac{\sum_{k}\alpha_{ik}Q_k}{\sum_{k}\alpha_{ik}}
\end{cases}
$$
Where $\alpha_{ik}$ is the threating coefficient, the bigger the values is, the heigher $k$ threatens $i$.

\begin{center}
\href{localhost:8888}{\large Demo}
\end{center}
}
\end{frame}
% subsection simple_demo (end)
\iffalse
\subsection{Reinforcement Learning and Control} % (fold)
\label{sub:reinforcement_learning_and_control}
\begin{frame}{Aim}{Reinforcement Learning}
\begin{block}{The aim}
\begin{itemize}
	\item Uncover the right action for user
	\item Uncover the right action for administrator to make adjustments
	\item From the view of user
	\item From the view of industrial chain
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Main Parts}{Reinforcement Learning}
\begin{block}{Main parts and steps}
\begin{itemize}
	\item Define states
	\item Design actions
	\item Set reward function
	\item Design state simulation
	\item Simulate
\end{itemize}
\end{block}
\end{frame}
\fi

### 2015-11-16 beamer/preliminary.tex
mutual rating
commit after come back

\subsection{Cloud Manufacturing}
\begin{frame}{Ecosystem Main Structure}{Cloud Manufacturing}
\only<1>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
	\caption{Princiapl Structure of Cloud Manufacturing Ecosystem}
	\end{figure}
}
\iffalse
\only<2>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=40 0 500 250,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\only<3>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=0 160 500 450,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\fi
\end{frame}

@@

\subsection{Roles}
\begin{frame}{Usual Names}{Roles}
\onslide<+->{\small
	\begin{description}
	\item[User] The main role in Cloud Manufacturing, usually acts as Seller or Buyer;
	\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service;
	\item[Buyer] The temporary role in a transaction, which submits the allocated part of manufacturing task;
	\item[Administrator] The role that gets the work for the operation and maintenance of the platform.
	\end{description}
}
\onslide<+->{
\begin{table}[htbp]
  \centering\scriptsize
    \begin{tabular}{lcc}
    \toprule
        &  Seller & Buyer  \\
    \midrule
    Generalized User & $\surd$ & $\surd$  \\
    Enterprise User & $\surd$ &  \\
    Customer User& & $\surd$ \\
    \bottomrule
    \end{tabular}%
\end{table}
}
\end{frame}

@@

\begin{frame}{User Rank}{Operating Model}
\onslide<+->{User Rank provides the basis to make the recommandation and to get more permission, the rank will increase or decrease by good or bad performance in each transaction}
\onslide<+->{
\begin{equation}
  \begin{cases}
      Rank_{[T+1]} = Rank_{[T]} + Gain - Lose, & T \geqslant 1\\
      Rank_{[0]} = Rank_{[init]}
  \end{cases}
\end{equation}
}
\end{frame}

\begin{frame}{Platform}{Operating Model}
\onslide<+->{
	Cloud Manufacturing Platform is mantained by Administrators with:
}
\onslide<+->{
	\begin{block}{Platform Maintenances}
	\begin{itemize}
	\item Decompose Orders into Tasks
	\item Construct Standard Services
	\item Introduce/Eliminate Users
	\item Distribute Permissions
	\item Adjust Resource Useage by Recommandations and Bonus
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Data Science Tools}
\begin{frame}{Data Science Tools}
\onslide<+->{In such Cloud Manufacturing Operating Model, there comes massive amount of data:\begin{itemize}
  \item Transaction histroy;
  \item Ranking histroy;
  \item Status of resources, services, orders and tasks;
  \item Decision pattern and so on.
\end{itemize}}
\onslide<+->{
	A bunch of Data Science Tools can be helpful:
	\begin{block}{Useful Data Science Tools}
	\begin{itemize}
	\item Data Analysis (collection, cleaning, modeling\&algorithms)
	\item Data Warehousing
	\item Machine Learning
	\item Social Network Anaysis
	\end{itemize}
	\end{block}
}
\end{frame}

%\begin{frame}{Blocks}
%\begin{block}{Block Title}
%You can also highlight sections of your presentation in a block, with it's own title
%\end{block}
%\begin{theorem}
%There are separate environments for theorems, examples, definitions and proofs.
%\end{theorem}
%\begin{example}
%Here is an example of an example block.
%\end{example}
%\end{frame}

>>>>

\subsection{Cloud Manufacturing}
\begin{frame}{Ecosystem Main Structure}{Cloud Manufacturing}
\only<1>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight]{figures/platformstruct.pdf}
	\caption{Principal Structure of Cloud Manufacturing Ecosystem}
	\end{figure}
}
\iffalse
\only<2>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=40 0 500 250,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\only<3>{
	\begin{figure}
	\centering
	\includegraphics[height=0.82\textheight,viewport=0 160 500 450,clip=true]{figures/platformstruct.pdf}
	\end{figure}
}
\fi
\end{frame}

@@

\subsection{Roles}
\begin{frame}{Usual Names}{Roles}
\onslide<+->{\small
	\begin{description}
	\item[User] The main role in Cloud Manufacturing, usually acts as a Seller or a Buyer;
	\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service;
	\item[Buyer] The temporary role in a transaction, which submits the allocated part of manufacturing task;
	\item[Administrator] The role that gets the work for the operation and maintenance of the platform.
	\end{description}
}
\onslide<+->{
\begin{table}[htbp]
  \centering\scriptsize
    \begin{tabular}{lcc}
    \toprule
        &  Seller & Buyer  \\
    \midrule
    Generalized User & $\surd$ & $\surd$  \\
    Enterprise User & $\surd$ &  \\
    Customer User& & $\surd$ \\
    \bottomrule
    \end{tabular}%
\end{table}
}
\end{frame}

@@

\begin{frame}{User Rank}{Operating Model}
\onslide<+->{
The recommendation for tasks or services will be easily permissible, if their owner got high user rank,
the rank will change for their performance in every transaction }
\onslide<+->{
\begin{equation}
  \begin{cases}
      Rank_{[T+1]} = Rank_{[T]} + Gain - Lose, & T \geqslant 1\\
      Rank_{[0]} = Rank_{[init]}
  \end{cases}
\end{equation}
}
\onslide<+->{
	This equation set shows a simple user rank change style for both a seller and a buyer.
}
\end{frame}

\begin{frame}{Rank Change}{Operating Model}
\onslide<+->{
	\begin{figure}
	\centering
	\includegraphics[trim=0 20 0 0,height=0.85\textheight]{figures/mutual.pdf}
	\caption{Mutual Evaluation for Input}
	\end{figure}
}
\end{frame}

\iffalse
\begin{frame}{Platform}{Operating Model}
\onslide<+->{
	Cloud Manufacturing Platform is mantained by Administrators with:
}
\onslide<+->{
	\begin{block}{Platform Maintenances}
	\begin{itemize}
	\item Decompose Orders into Tasks
	\item Construct Standard Services
	\item Introduce/Eliminate Users
	\item Distribute Permissions
	\item Adjust Resource Useage by Recommandations and Bonus
	\end{itemize}
	\end{block}
}
\end{frame}

\subsection{Data Science Tools}
\begin{frame}{Data Science Tools}
\onslide<+->{In such Cloud Manufacturing Operating Model, there comes massive amount of data:\begin{itemize}
  \item Transaction histroy;
  \item Ranking histroy;
  \item Status of resources, services, orders and tasks;
  \item Decision pattern and so on.
\end{itemize}}
\onslide<+->{
	A bunch of Data Science Tools can be helpful:
	\begin{block}{Useful Data Science Tools}
	\begin{itemize}
	\item Data Analysis (collection, cleaning, modeling\&algorithms)
	\item Data Warehousing
	\item Machine Learning
	\item Social Network Anaysis
	\end{itemize}
	\end{block}
}
\end{frame}
\fi
%\begin{frame}{Blocks}
%\begin{block}{Block Title}
%You can also highlight sections of your presentation in a block, with it's own title
%\end{block}
%\begin{theorem}
%There are separate environments for theorems, examples, definitions and proofs.
%\end{theorem}
%\begin{example}
%Here is an example of an example block.
%\end{example}
%\end{frame}

### 2015-11-16 beamer/schedule.tex
commit after come back

% !TEX root = ../beamer.tex
\section{Services Scheduling}
\subsection{Standardization}
\begin{frame}{Support Module}{Service Standardization}
\onslide<+->{The basic support modules for Service Standardization include:
\begin{block}{Basic Modules}
\begin{itemize}
\item Resource Virtualization \& Encapsulation
\item Clustering Method
\item Refine Method
\end{itemize}
\end{block}}

\onslide<+->{
Important support Service Scheduling process modules:
\begin{block}{Support Moudles}
\begin{itemize}
\item Decision Making Support
\item Matching Regualtion
\item Platform Assistance
\end{itemize}
\end{block}
}
\end{frame}

\subsection{Decision Making Support}
\begin{frame}{Decision Making Support}{Services Scheduling}
\onslide<+->{
	Users in Cloud Manufacturing platfrom will make decision for:
}
\onslide<+->{
	\begin{itemize}
	\item Order acceptance;
	\item Task decomposition;
	\item Task (re-)outsourscing;
	\item Seller selection;
	\item Manufacturing arrangement.
	\end{itemize}
}
\end{frame}

@@

\subsection{Platform Assistance}
\begin{frame}{Platform Assistance}{Services Scheduling}
\onslide<+->{
	Administrator assist platform to set priority for tasks and services, so the user will considerd:
}
\onslide<+->{
	\begin{itemize}
	\item How to make priority setting recommendation
	\item How to make decisions with the recommendation
	\end{itemize}
}
\end{frame}

>>>>

% !TEX root = ../beamer.tex
\section{Services Scheduling}
\subsection{Standardization}
\begin{frame}{Support Module}{Service Standardization}
\onslide<+->{The basic support modules for Service Standardization include:
\begin{block}{Basic Modules}
\begin{itemize}
\item Resource Virtualization \& Encapsulation
\item Clustering Method
\item Imporvement Method
\end{itemize}
\end{block}}

\onslide<+->{
Important support Service Scheduling process modules:
\begin{block}{Support Modules}
\begin{itemize}
\item Decision Making Support
\item Matching Regualtion
\item Platform Assistance
\end{itemize}
\end{block}
}
\end{frame}

\subsection{Decision Making Support}
\begin{frame}{Decision Making Support}{Services Scheduling}
\onslide<+->{
	Decisions that users make in Cloud Manufacturing platform include:
}
\onslide<+->{
	\begin{itemize}
	\item Order acceptance;
	\item Task decomposition;
	\item Task (re-)outsourscing;
	\item Seller selection;
	\item Manufacturing arrangement.
	\end{itemize}
}
\end{frame}

@@

\subsection{Platform Assistance}
\begin{frame}{Platform Assistance}{Services Scheduling}
\onslide<+->{
	Administrator assists platform to set priority for taks or services, so two aspects should be considered for users:
}
\onslide<+->{
	\begin{itemize}
	\item How to make priority setting recommendation
	\item How to make decisions with the recommendation
	\end{itemize}
}
\end{frame}
